A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2017-03-27 casm.tex
Comentario 1 revisor 3, integrado.

In the context of our model, utility represents
  access to resources shared by others.
  The value of the utility function for a player is the sum of the payoffs of playing
  with its neighbors. The opposing force comes from the other concurrent game: players
  trying to maximize the strength of their interactions with other players. In the coordination game
  the best strategy is to adopt the same strategy as the other player, as it pays the most,
  regardless of cooperation or defection in the utility game. When
  both cooperate the interaction gets a positive payoff, when both defect, the
  interaction doesn't get affected; but if they do not coordinate, then the
  interaction loses. Finally, cooperation is a central feature of scientific work.
  For our biomedical network, cooperation can be thought of
  as sharing resources such as time, students, equipment, even money. Examples of defection
  to a cooperator are ghost authorship or
  prestige authorship.\\

@@

After each game, the agent adds up utility ($u$), which is the sum of the
payoffs following the PD matrix. A pair of neighbors will add or substract from the strength of
their interaction ($w_{ji}$) as they coordinate or not, being $w$
also cumulative. We measure global utility and strength of interaction for the whole
network. Global utility $U$ is the sum of all individual utilities and global
strength of interaction or $W$ is the sum of every pair of agents' links
$w$. The strength of interaction can be thought of as some sort of ``trust''.\\

>>>>

In the context of our model, utility represents
  access to resources shared by others.
  The value of the utility function for a player is the sum of the payoffs of playing
  with its neighbors. The opposing force comes from the other concurrent game: players
  trying to maximize the strength of their interactions with other players.

%%Strength of connection may have different meaning. From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project. From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of trust among them. But this may not be the only interpreation since it can depend on each case. For instance students are expected to collaborate with their advisors, still there can be cases in which students are subdued to collaborate with them. In such a case, instead of trust there would be an asymmetry of power. This situation may not be limited to advisor-students relationships; we are aware of cases between a politically powerful scientist “recruting” other scientists that are somehow obligated to collaborate with them. The risk of refusing to collaborate in this situation can represent a politically bad move.

%%Since the strength of connection can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers. Still we are aware that naming strength of connection to the number of times scientists collaborate, can be quite abstract and it needs to be expressed in more concrete ways. In the coordination game
  the best strategy is to adopt the same strategy as the other player, as it pays the most,
  regardless of cooperation or defection in the utility game. When
  both cooperate the interaction gets a positive payoff, when both defect, the
  interaction doesn't get affected; but if they do not coordinate, then the
  interaction loses. Finally, cooperation is a central feature of scientific work.
  For our biomedical network, cooperation can be thought of
  as sharing resources such as time, students, equipment, even money. Examples of defection
  to a cooperator are ghost authorship or
  prestige authorship.\\

@@

After each game, the agent adds up utility ($u$), which is the sum of the
payoffs following the PD matrix. A pair of neighbors will add or substract from the strength of
their interaction ($w_{ji}$) as they coordinate or not, being $w$
also cumulative. We measure global utility and strength of interaction for the whole
network. Global utility $U$ is the sum of all individual utilities and global
strength of interaction or $W$ is the sum of every pair of agents' links
$w$. Strength of interaction may have different meanings. From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project. From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of "trust" among them. But this may not be the only possible interpreation since it can be different for each case. Since the strength of interactions can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers. \\
